\plaintitle

### 2016-09-21 drafts/labor/discussion.tex
wait is discussion being committed?

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Implications for Research}
\begin{enumerate}
  \item \ali{the past is no guarantee of the future; what could be unforeseen?
  \item it's easy to fall into the (dys|u)--topian camp of what piecework/crowd work will look like
  \item what should we be focusing on? the future of crowd work}
\end{enumerate}

>>>>

\documentclass[trackingWork]{subfiles}
\makeatletter
\def\blx@maxline{77}
\makeatother
\begin{document}
\section{Discussion}
\topic{Having taken a comprehensive look toward crowd work through the piecework lens,
we can't help but take a step back to consider a number of meta--issues that arose in our analysis.}

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}

\subsection{Polarizing Tendencies}\label{sec:polarizationOfCrowdWork}

\subsection{Taking Stock of our Research Agenda}\label{sec:whatShouldBeTheFuture}

\begin{enumerate}
  \item \ali{the past is no guarantee of the future; what could be unforeseen?
  \item it's easy to fall into the (dys|u)--topian camp of what piecework/crowd work will look like
  \item what should we be focusing on? the future of crowd work}
\end{enumerate}
